Codes for Figure 4

### 2021-03-16 code_for_figure4.Rmd
add codes for calculating posterior mean and 95% credible intervals for log2(fold change)

respiration_1_plate <- convert_ocr_to_respiration(scenario_1_plate, experiment_setup)
#respiration_1_plate$scenario <- "1 plate"
respiration_1_plate$plate_id <- "20130930_1109"
```

@@

respiration_2_plates <- convert_ocr_to_respiration(scenario_2_plates, experiment_setup)
respiration_2_plates$plate_id <- "20140202_1849"
```

@@

respiration_3_plates <- convert_ocr_to_respiration(scenario_3_plates, experiment_setup)
respiration_3_plates$plate_id <- "20140205_1620"
```

@@

respiration_3_plates_combine <- convert_ocr_to_respiration(scenario_3_plates, experiment_setup)
respiration_3_plates_combine$plate_id <- "3 Plates Combined"
```

>>>>

respiration_1_plate <- convert_ocr_to_respiration(scenario_1_plate, experiment_setup)
#respiration_1_plate$scenario <- "1 plate"
respiration_1_plate$plate_id <- "20130930_1109"

respiration_1_plate %>% 
  spread(Cell_line, val) %>% 
  dplyr::mutate(diff_in_respir = log2(`61818`) - log2(NHDF)) %>% 
  dplyr::group_by(what) %>% 
  summarize(post_mean = mean(diff_in_respir), 
            low_mean = quantile(diff_in_respir, probs = 0.025), 
            high_mean = quantile(diff_in_respir, probs = 0.975))
```

@@

respiration_2_plates <- convert_ocr_to_respiration(scenario_2_plates, experiment_setup)
respiration_2_plates$plate_id <- "20140202_1849"

respiration_2_plates %>% 
  spread(Cell_line, val) %>% 
  dplyr::mutate(diff_in_respir = log2(`61818`) - log2(NHDF)) %>% 
  dplyr::group_by(what) %>% 
  summarize(post_mean = mean(diff_in_respir), 
            low_mean = quantile(diff_in_respir, probs = 0.025), 
            high_mean = quantile(diff_in_respir, probs = 0.975))
```

@@

respiration_3_plates <- convert_ocr_to_respiration(scenario_3_plates, experiment_setup)
respiration_3_plates$plate_id <- "20140205_1620"

respiration_3_plates %>% 
  spread(Cell_line, val) %>% 
  dplyr::mutate(diff_in_respir = log2(`61818`) - log2(NHDF)) %>% 
  dplyr::group_by(what) %>% 
  summarize(post_mean = mean(diff_in_respir), 
            low_mean = quantile(diff_in_respir, probs = 0.025), 
            high_mean = quantile(diff_in_respir, probs = 0.975))
```

@@

respiration_3_plates_combine <- convert_ocr_to_respiration(scenario_3_plates, experiment_setup)
respiration_3_plates_combine$plate_id <- "3 Plates Combined"

respiration_3_plates_combine %>% 
  spread(Cell_line, val) %>% 
  dplyr::mutate(diff_in_respir = log2(`61818`) - log2(NHDF)) %>% 
  dplyr::group_by(what) %>% 
  summarize(post_mean = mean(diff_in_respir), 
            low_mean = quantile(diff_in_respir, probs = 0.025), 
            high_mean = quantile(diff_in_respir, probs = 0.975))
```
